Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2018-01-18 paper/paper.Rmd

The Australian Open conducts matches on a range of courts, as some of these courts are located outdoors it is common to see accessories worn by players. Glasses, visors, hats, sweatbands and other additional pieces are worn by players, especially during day matches played outside. Table \@ref(tab:accessories) shows the accessories associated with a manually tagged face. It can be seen that most faces captured were not wearing glasses, however there were a similar amount of faces captured with and without head wear.

@@

table(afm$glasses, afm$type) %>% as.matrix() -> glassesTab

>>>>

The use of accessories like glasses and head wear, visors or hats, is common during the Australian Open as play is mostly outdoors during daytime.  Table \@ref(tab:accessories) shows player use of head wear and glasses, as tagged manually. Table \@ref(tab:glasses) compares the face capture rate of the different APIs for the player acessories.

of the proportions tells that of the faces wearing glasses, there were a similar amount of faces captured with and without head wear. Of those without glasses only 26% wore head wear. This may be influenced by weather and sunlight on the court during Australian Open matches.

@@

table(afm$visorhat, afm$type) %>% as.matrix() -> glassesTab
